---
title: "Moderated mediation for ELS pipline"
output: html_document
---
### basic setup

```{r}
library(dplyr)
library(rosetta)
library(ggplot2)
library(lavaan)
library(semTools)
library(fastDummies)
setwd('~/Desktop/COGGPS_PAPER/final_ver')
```

### extracting morphology brain features 

```{r}

###data prep
mor<-read.csv(file ='mor_final.csv')
pheno<-read.csv(file='final_phenotype_for_MM_european.csv')
#pheno<-pheno[pheno$sex==1,]
#pheno<-pheno[pheno$sex==1,]
#mor$subjectkey<-gsub("_","",mor$subjectkey)
MERGED<-merge(pheno,mor,by='subjectkey')
#MERGED<-na.omit(MERGED)

COV_LIST <- c('age', 'sex','high.educ', 'income', 'married',,'abcd_site', 'BMI') # should be checked
fact_COV_LIST <- c('age','sex' ,'high.educ', 'income' ,'factor(married)','factor(abcd_site)', 'BMI') # should be checked

print(fact_COV_LIST)
COVARS <- paste(fact_COV_LIST, collapse=" + ")
GPS_LIST<-c('CP','EA')


names(MERGED)[43]
BRAIN_START = 43
BRAIN_END <- length(MERGED)
NUM_GPS <- length(GPS_LIST)

BETA_LIST <- c( 'beta_brain')
P_LIST <- c( 'p_brain')

###calculating
for (j in 1:2){
  for (gps in GPS_LIST[[j]]){
    print(paste('--------------',gps,'--------------'))
    # initialize all vector
    brain <- vector()
    
    glm.se <- vector()
    glm.beta <- data.frame()
    glm.p <- data.frame()
    
    # DO GLM
    for (i in BRAIN_START:BRAIN_END){
      print(i)
      brain <- c(brain, names(MERGED)[i])
      
      form <- paste(names(MERGED)[i], '~',gps,'+' ,COVARS)
      
      glm.re <- glm(as.formula(form), data=MERGED, family=gaussian())
      cff <- coef(summary(glm.re))
      glm.se <- c(glm.se, round(cff[2, 2], 5))
      glm.beta <- rbind.data.frame(glm.beta, cff[2,1])
      glm.p <- rbind.data.frame(glm.p, cff[2,4])
      
      
    }
    colnames(glm.beta) <- BETA_LIST
    colnames(glm.p) <- P_LIST
    result <- data.frame(brain, glm.beta, glm.p)
    result <- result[-which(duplicated(result$p_brain)),]
    BONF<-p.adjust(result$p_brain,method='bonferroni')
    result<-cbind(result,BONF)
    FILE_NAME <- paste0('~/Desktop/GLM_mor_cov_', gps, '_prsice2_corrected.csv')
    write.csv(result, FILE_NAME, quote = F,row.names = F)
    
    
  }
  
} 

```

###list significant brain features

```{r}
### making significant list 
brainList<-function(target){
  brain_list<-c()
  for (i in 1:nrow(target)){
    if (target[i,'BONF']<0.05){
      brain_list<-rbind(brain_list,target[i,])
    }
  }

  file_name<-paste0('~/Desktop/',deparse(substitute(target)),'_brain_list.csv')

  write.csv(brain_list,file_name,row.names = F,quote = F)
}

CP_related<-read.csv('~/Desktop/GLM_mor_cov_CP_prsice2_corrected.csv')
EA_related<-read.csv('~/Desktop/GLM_mor_cov_EA_prsice2_corrected.csv')

brainList(CP_related)
brainList(EA_related)

```


###PCA with significant brain features

```{r}
mor<-read.csv(file='mor_final.csv')
CP<-read.csv(file='~/Desktop/CP_related_brain_list.csv')
EA<-read.csv(file='~/Desktop/EA_related_brain_list.csv')

## prep
subject_list<-read.csv(file='final_phenotype_for_MM_european.csv')
#subject_list<-subject_list[subject_list$sex==1,]
#subject_list<-subject_list[subject_list$sex==2,]
mor$subjectkey<-gsub("_","",mor$subjectkey)


mor<-merge(mor,subject_list,by='subjectkey')

mor<-na.omit(mor)
names(mor)[996] #before running PCA must check column number of brain end
brain_end<-996
mor<-mor[,1:brain_end]




####+++++ operation
CP_extract<-CP[CP$BONF<0.05,]
CP_list<-CP_extract$brain
CP_mor<-subset(mor,select=c('subjectkey',CP_list))
CP_mor<-merge(subject_list,mor,by='subjectkey')
CP_mor<-subset(CP_mor,select=c('subjectkey',CP_list))


EA_extract<-EA[EA$BONF<0.05,]
EA_list<-EA_extract$brain
EA_mor<-subset(mor,select=c('subjectkey',EA_list))
EA_mor<-merge(subject_list,mor,by='subjectkey')
EA_mor<-subset(EA_mor,select=c('subjectkey',EA_list))



#save
write.csv(CP_mor,file='CP_mor_extracted.csv',row.names=FALSE)
write.csv(EA_mor,file='EA_mor_extracted.csv',row.names=FALSE)


######By performing PCA, reduce statistically significant brain variables. And assign Principal Component(reduced brain variable) to subjects 
CP_mor_filled<-CP_mor
subjectkey<-CP_mor_filled[,1]
CP_mor_filled_pca<-CP_mor_filled[,-1]  ##remove subjectkey column for PCA
CP_pca<-prcomp(CP_mor_filled_pca,center=T,scale. = T)
CP_pca_var<-as.matrix(CP_mor_filled_pca)%*%CP_pca$rotation[,1:10]#check cumulative Proportion to select how many PCs you need
CP_PC_transformed<-cbind(subjectkey,as.data.frame(CP_pca_var))
for(i in 2:ncol(CP_PC_transformed)){
  CP_PC_transformed[,i]<-scale(CP_PC_transformed[,i])
}
CP_PC_transformed$PC1 <- -1*CP_PC_transformed$PC1

EA_mor_filled<-EA_mor
subjectkey<-EA_mor_filled[,1]
EA_mor_filled_pca<-EA_mor_filled[,-1]  ##remove subjectkey column for PCA
EA_pca<-prcomp(EA_mor_filled_pca,center=T,scale. = T)
EA_pca_var<-as.matrix(EA_mor_filled_pca)%*%EA_pca$rotation[,1:10]#check cumulative Proportion to select how many PCs you need
EA_PC_transformed<-cbind(subjectkey,as.data.frame(EA_pca_var))
for(i in 2:ncol(EA_PC_transformed)){
  EA_PC_transformed[,i]<-scale(EA_PC_transformed[,i])
}

##save
write.csv(CP_PC_transformed,file='~/Desktop/CP_PCA_transformed.csv',row.names=FALSE)
write.csv(EA_PC_transformed,file='~/Desktop/EA_PCA_transformed.csv',row.names=FALSE)


```

### before mediation modeling must check correlations between variables 
#1: GPS-NIH
```{r}
#list for independent variable
GPS_list<-c('CP','EA')

#list for dependent variable
nih_list<-c('nihtbx_totalcomp_uncorrected',	'nihtbx_fluidcomp_uncorrected',	'nihtbx_cryst_uncorrected')

#list for covariate variable
cat_var<-c('sex','married' , 'abcd_site')
con_var<-c('age','high.educ','income','BMI')

#join all list for dataset
all_list<-c('subjectkey')
all_list<-append(all_list,nih_list)
all_list<-append(all_list,cat_var)
all_list<-append(all_list,con_var)
all_list<-append(all_list,GPS_list)
#all_list<-append(all_list,PRS_COV_LIST)

#loading datatset
data<-read.csv(file='final_phenotype_for_MM_european.csv')
data<-data[,all_list]
#data<-data[data$sex==1,]
#data<-data[data$sex==2,]



#appending categorical and continuous covariates together 
#cat_var<-cat_var[-1] only use for sex stratified analysis
cov_list<-c()
for (i in cat_var){
  cov_list<-append(cov_list,paste0("factor(",i,")"))
}
cov_list<-append(cov_list,con_var)
cov<- paste(cov_list, collapse=" + ")



#glm 
frame<-data.frame(nih_list)
for (GPS in GPS_list){
  glm.p<-vector()
  glm.p.adjust<-vector()
  glm.beta<-vector()
  for (nih_name in nih_list) {
    
    form<-paste(nih_name,'~',GPS,'+',cov)
    glm.re<-glm(as.formula(form),data=data,family=gaussian())
    cff<-coef(summary(glm.re))
    glm.p<-append(glm.p,round(cff[2,4],5))
    glm.beta<-append(glm.beta,round(cff[2,1],5))
    
  }
  
  glm.p.adjust<-p.adjust(glm.p,method='bonf')
  beta_name<-paste0(GPS,'_beta')
  beta<-data.frame(glm.beta)
  names(beta)<-beta_name
  frame<-cbind(frame,beta)
  p_name<-paste0(GPS,'_p')
  p_name.adjust<-paste0(GPS,'_p_bonf_corrected')
  p_values<-data.frame(glm.p)
  p_values_cor<-data.frame(glm.p.adjust)
  names(p_values)<-p_name
  names(p_values_cor)<-p_name.adjust
  frame<-cbind(frame,p_values)
  frame<-cbind(frame,p_values_cor)
}

#saving
write.csv(frame,file='~/Desktop/GPS-NIH_glm_bonf.csv',row.names=FALSE)

```

#2: PC-NIH
```{r}
#=========checking correlation between compressed brain variables and phenotypes 
###preprocessing data
#
all_list<-c('subjectkey','CP','EA','age', 'sex', 'high.educ','income','married' ,'abcd_site', 'BMI','nihtbx_totalcomp_uncorrected',	'nihtbx_fluidcomp_uncorrected',	'nihtbx_cryst_uncorrected')
nih_list<-c('nihtbx_totalcomp_uncorrected',	'nihtbx_fluidcomp_uncorrected',	'nihtbx_cryst_uncorrected')
cat_var<-c( 'sex','married','abcd_site')
con_var<-c('age','high.educ','income','BMI')


#appending categorical and continuous variable together 
cov_list<-c()
for (i in cat_var){
  cov_list<-append(cov_list,paste0("factor(",i,")"))
}
cov_list<-append(cov_list,con_var)
cov<- paste(cov_list, collapse=" + ")


CP_PC_transformed<-read.csv(file='~/Desktop/CP_PCA_transformed.csv')

EA_PC_transformed<-read.csv(file='~/Desktop/EA_PCA_transformed.csv')
data<-read.csv(file='final_phenotype_for_MM_european.csv')
data<-data[,all_list]
data<-na.omit(data) ## this line is for removing subjects with NA values. If you don't want to remove NA, then disable this line 

CP_data<-merge(CP_PC_transformed,data,by='subjectkey')
EA_data<-merge(EA_PC_transformed,data,by='subjectkey')



#CP_data<-CP_data[CP_data$sex==1,]
#EA_data<-EA_data[EA_data$sex==1,]
#CP_data<-CP_data[CP_data$sex==2,]
#EA_data<-EA_data[EA_data$sex==2,]

###glm for CP
CP_frame<-data.frame(nih_list)
for (i in 1:10){ #####checking numbers of PC
  glm.p<-vector()
  glm.p.adjust<-vector()
  glm.beta<-vector()
  
  for (nih_name in nih_list) {
    
    form<-paste0(nih_name,'~','PC',i,'+',cov)
    glm.re<-glm(as.formula(form),data=CP_data,family=gaussian())
    cff<-coef(summary(glm.re))
    glm.p<-append(glm.p,round(cff[2,4],6))
    glm.p.adjust<-p.adjust(glm.p,method='bonf')###fdr correction
    glm.beta<-append(glm.beta,round(cff[2,1],6))
  }
  p_values<-data.frame(glm.p)
  p_values_cor<-data.frame(glm.p.adjust)
  beta<-data.frame(glm.beta)
  col_name_p<-paste0('PC',i,'_p')
  col_name_p_cor<-paste0('PC',i,'_p_cor')
  col_name_beta<-paste0('PC',i,'_beta')
  names(p_values)<-col_name_p
  names(p_values_cor)<-col_name_p_cor
  names(beta)<-col_name_beta
  CP_frame<-cbind(CP_frame,p_values)
  CP_frame<-cbind(CP_frame,p_values_cor)
  CP_frame<-cbind(CP_frame,beta)
}

###glm for EA
EA_frame<-data.frame(nih_list)
for (i in 1:10){ #####checking numbers of PC
  glm.p<-vector()
  glm.p.adjust<-vector()
  glm.beta<-vector()
  
  for (nih_name in nih_list) {
    
    form<-paste0(nih_name,'~','PC',i,'+',cov)
    glm.re<-glm(as.formula(form),data=EA_data,family=gaussian())
    cff<-coef(summary(glm.re))
    glm.p<-append(glm.p,round(cff[2,4],6))
    glm.p.adjust<-p.adjust(glm.p,method='bonf')###fdr correction
    glm.beta<-append(glm.beta,round(cff[2,1],6))
  }
  p_values<-data.frame(glm.p)
  p_values_cor<-data.frame(glm.p.adjust)
  beta<-data.frame(glm.beta)
  col_name_p<-paste0('PC',i,'_p')
  col_name_p_cor<-paste0('PC',i,'_p_cor')
  col_name_beta<-paste0('PC',i,'_beta')
  names(p_values)<-col_name_p
  names(p_values_cor)<-col_name_p_cor
  names(beta)<-col_name_beta
  EA_frame<-cbind(EA_frame,p_values)
  EA_frame<-cbind(EA_frame,p_values_cor)
  EA_frame<-cbind(EA_frame,beta)
}


write.csv(CP_frame,file='~/Desktop/CP_PC(mor)-pheno_glm.csv',row.names=FALSE)
write.csv(EA_frame,file='~/Desktop/EA_PC(mor)-pheno_glm.csv',row.names=FALSE)

```


### checking moderation with suspicious moderator in Moderated Mediation 
##1: checking moderation 
#loading and preprocessing data
```{r}
## change categorical variable (K>2) to dummy variable
pheno<-read.csv(file='final_phenotype_for_MM_european.csv')

##merge brain data and phenotype data 
CP_brain<-read.csv(file='~/Desktop/CP_PCA_transformed.csv')
CP_brain<-subset(CP_brain,select=c('subjectkey','PC1'))   ######brain target
CP_final<-merge(pheno,CP_brain,by='subjectkey')
##check remaining NA
CP_final<-na.omit(CP_final)
#CP_final<-CP_final[CP_final$sex==1,]
#CP_final<-CP_final[CP_final$sex==2,]

EA_brain<-read.csv(file='~/Desktop/EA_PCA_transformed.csv')
EA_brain<-subset(EA_brain,select=c('subjectkey','PC1'))   ######brain target
EA_final<-merge(pheno,EA_brain,by='subjectkey')
###check remaining NA
EA_final<-na.omit(EA_final)
#EA_final<-EA_final[EA_final$sex==1,]
#EA_final<-EA_final[EA_final$sex==2,]
```

#defining function for moderation
```{r}
moderation<-function(GPS,cog_target,ELS_list,data){
  list<-paste(GPS,"&",ELS_list)
  
  
  ##=============first step. only ELS
  COG<-paste0("nihtbx_",cog_target,"_uncorrected")
  frame<-data.frame(ELS_list)
  glm.p<-vector()
  glm.beta<-vector()
  for (ELS in ELS_list) {
    form<-paste(COG,"~ ",GPS,"+",ELS,"+",cov)
    result<-glm(as.formula(form),data=data,family=gaussian())
    cff<-coef(summary(result))
    glm.p<-append(glm.p,round(cff[3,4],5))
    glm.beta<-append(glm.beta,round(cff[3,1],5))
  }
  
  beta<-data.frame(glm.beta)
  names(beta)<-"beta"
  frame<-cbind(frame,beta)
  p_values<-data.frame(glm.p)
  names(p_values)<-"p_value"
  frame<-cbind(frame,p_values)
  bonf<-p.adjust(glm.p,method="bonf")
  bonf<-data.frame(bonf)
  names(bonf)<-'p_bonf_ corrected'
  frame<-cbind(frame,bonf)
  
  ##=============second step. with interaction
  frame_inter<-data.frame(list)
  glm.p<-vector()
  glm.beta<-vector()
  for (ELS in ELS_list) {
    interaction_term<-paste0(GPS,".",ELS)
    interaction_var <- data[,GPS]*data[,ELS]
    data <- cbind(data,interaction_var)
    colnames(data)[ncol(data)] <- interaction_term
    form<-paste(COG,"~ ",GPS,"+",interaction_term,"+",ELS,"+",cov)
    result<-glm(as.formula(form),data=data,family=gaussian())
    cff<-coef(summary(result))
    #print(cff)
    glm.p<-append(glm.p,round(cff[3,4],5))
    glm.beta<-append(glm.beta,round(cff[3,1],5))
  }
  
  beta<-data.frame(glm.beta)
  names(beta)<-"beta"
  frame_inter<-cbind(frame_inter,beta)
  p_values<-data.frame(glm.p)
  names(p_values)<-"p_value"
  frame_inter<-cbind(frame_inter,p_values)
  bonf<-p.adjust(glm.p,method="bonf")
  bonf<-data.frame(bonf)
  names(bonf)<-'p_bonf_ corrected'
  frame_inter<-cbind(frame_inter,bonf)
  
  final<-cbind(frame,frame_inter)
  
  file_name<-paste0('~/Desktop/',GPS,'*ELS_',cog_target,'_moderate.csv')
  write.csv(final,file=file_name,row.names=F,quote = F)
  
  
}
```

#checking moderation. must check ELS_list, covariate list, intelligence list
```{r}
#setting ELS list
ELS_list<-c("Ab","Ne","HC_all")
#ELS_list <- c("HC_PSD","HC_CHM","HC_HSA","HC_MIH","HC_MTV","Ab_SA","Ab_PA","Ne_EN","Ne_PN")
  #colnames(pheno)[29:37]

#setting covariate list
cat_var<-c( 'sex', 'married', 'abcd_site')
con_var<-c('age','high.educ','income','BMI')
cov_list<-c()

#appending categorical and continuousv ariable together
cov_list<-append(cov_list,con_var)
cov<- paste(cov_list, collapse=" + ")


#setting intelligence list
intel_list<-c('cryst','totalcomp','fluidcomp')


#analyzing for CP 
GPS<-"CP"
data<-CP_final
for (intel in intel_list){
  moderation(GPS,intel,ELS_list,data=data)
}

#analyzing for EA 
GPS<-"EA"
data<-EA_final
for (intel in intel_list){
  moderation(GPS,intel,ELS_list,data=data)
}

```




##2: mediation and moderated mediation 
#data loading and prep 
```{r}

```


#running mediation 
```{r}
source('/work2/07939/tg872382/stampede2/connectome/stampede2/cognitive_GPS/Mediation_function.R')

ELS_list <- c("Ab","Ne","HC_all")
nih_list <- c("nihtbx_totalcomp_uncorrected","nihtbx_fluidcomp_uncorrected","nihtbx_cryst_uncorrected")


EA_cryst <- EA_Mediation("nihtbx_cryst_uncorrected",1000)
print("EA_cryst done")
EA_total <- EA_Mediation("nihtbx_totalcomp_uncorrected",1000)
print("EA_total done")
EA_fluid <- EA_Mediation("nihtbx_fluidcomp_uncorrected",1000)
print("EA_fluid done")
save.image('/work2/07939/tg872382/stampede2/connectome/stampede2/cognitive_GPS/Mediation_Experiment.RData')

CP_cryst <- CP_Mediation("nihtbx_cryst_uncorrected",1000)
print("CP_cryst done")
CP_total <- CP_Mediation("nihtbx_totalcomp_uncorrected",1000)
print("CP_total done")
CP_fluid <- CP_Mediation("nihtbx_fluidcomp_uncorrected",1000)
print("CP fluid done")


save.image('/work2/07939/tg872382/stampede2/connectome/stampede2/cognitive_GPS/Mediation_Experiment.RData')

```

#running moderated mediation. Main scale
```{r}
## === A path === ##
source('/work2/07939/tg872382/stampede2/connectome/stampede2/cognitive_GPS/MM_function.R')

ELS_list <- c("Ab","Ne","HC_all")
nih_list <- c("nihtbx_totalcomp_uncorrected","nihtbx_fluidcomp_uncorrected","nihtbx_cryst_uncorrected")


EA_Ab_cryst <- EA_Moderated_Mediation("nihtbx_cryst_uncorrected","Ab",1000)
print("EA_Ab_cryst done")
EA_Ab_total <- EA_Moderated_Mediation("nihtbx_totalcomp_uncorrected","Ab",1000)
print("EA_Ab_total done")
EA_Ab_fluid <- EA_Moderated_Mediation("nihtbx_fluidcomp_uncorrected","Ab",1000)
print("EA_Ab_fluid done")


EA_Ne_cryst <- EA_Moderated_Mediation("nihtbx_cryst_uncorrected","Ne",1000)
print("EA_Ne_cryst done")
EA_Ne_total <- EA_Moderated_Mediation("nihtbx_totalcomp_uncorrected","Ne",1000)
print("EA_Ne_total done")
EA_Ne_fluid <- EA_Moderated_Mediation("nihtbx_fluidcomp_uncorrected","Ne",1000)
print("EA_Ne_fluid done")

EA_HC_all_cryst <- EA_Moderated_Mediation("nihtbx_cryst_uncorrected","HC_all",1000)
print("EA_HC_all_cryst done")
EA_HC_all_total <- EA_Moderated_Mediation("nihtbx_totalcomp_uncorrected","HC_all",1000)
print("EA_HC_all_total done")
EA_HC_all_fluid <- EA_Moderated_Mediation("nihtbx_fluidcomp_uncorrected","HC_all",1000)
print("EA_HC_all_fluid done")
save.image('/work2/07939/tg872382/stampede2/connectome/stampede2/cognitive_GPS/Experiment.RData')

CP_Ab_cryst <- CP_Moderated_Mediation("nihtbx_cryst_uncorrected","Ab",1000)
print("CP_Ab_cryst done")
CP_Ab_total <- CP_Moderated_Mediation("nihtbx_totalcomp_uncorrected","Ab",1000)
print("CP_Ab_total done")
CP_Ab_fluid <- CP_Moderated_Mediation("nihtbx_fluidcomp_uncorrected","Ab",1000)
print("CP_Ab_fluid done")


CP_Ne_cryst <- CP_Moderated_Mediation("nihtbx_cryst_uncorrected","Ne",1000)
print("CP_Ne_cryst done")
CP_Ne_total <- CP_Moderated_Mediation("nihtbx_totalcomp_uncorrected","Ne",1000)
print("CP_Ne_total done")
CP_Ne_fluid <- CP_Moderated_Mediation("nihtbx_fluidcomp_uncorrected","Ne",1000)
print("CP_Ne_fluid done")

CP_HC_all_cryst <- CP_Moderated_Mediation("nihtbx_cryst_uncorrected","HC_all",1000)
print("CP_HC_all_cryst done")
CP_HC_all_total <- CP_Moderated_Mediation("nihtbx_totalcomp_uncorrected","HC_all",1000)
print("CP_HC_all_total done")
CP_HC_all_fluid <- CP_Moderated_Mediation("nihtbx_fluidcomp_uncorrected","HC_all",1000)
print("CP_HC_all_fluid done")

save.image('/work2/07939/tg872382/stampede2/connectome/stampede2/cognitive_GPS/Experiment.RData')

print('all done')

## ============= ##

## === B path === ##
source('/work2/07939/tg872382/stampede2/connectome/stampede2/cognitive_GPS/MM_function_Bpath.R')

ELS_list <- c("Ab","Ne","HC_all")
nih_list <- c("nihtbx_totalcomp_uncorrected","nihtbx_fluidcomp_uncorrected","nihtbx_cryst_uncorrected")


EA_Ab_cryst <- EA_Moderated_Mediation("nihtbx_cryst_uncorrected","Ab",1000)
print("EA_Ab_cryst done")
EA_Ab_total <- EA_Moderated_Mediation("nihtbx_totalcomp_uncorrected","Ab",1000)
print("EA_Ab_total done")
EA_Ab_fluid <- EA_Moderated_Mediation("nihtbx_fluidcomp_uncorrected","Ab",1000)
print("EA_Ab_fluid done")


EA_Ne_cryst <- EA_Moderated_Mediation("nihtbx_cryst_uncorrected","Ne",1000)
print("EA_Ne_cryst done")
EA_Ne_total <- EA_Moderated_Mediation("nihtbx_totalcomp_uncorrected","Ne",1000)
print("EA_Ne_total done")
EA_Ne_fluid <- EA_Moderated_Mediation("nihtbx_fluidcomp_uncorrected","Ne",1000)
print("EA_Ne_fluid done")

EA_HC_all_cryst <- EA_Moderated_Mediation("nihtbx_cryst_uncorrected","HC_all",1000)
print("EA_HC_all_cryst done")
EA_HC_all_total <- EA_Moderated_Mediation("nihtbx_totalcomp_uncorrected","HC_all",1000)
print("EA_HC_all_total done")
EA_HC_all_fluid <- EA_Moderated_Mediation("nihtbx_fluidcomp_uncorrected","HC_all",1000)
print("EA_HC_all_fluid done")
save.image('/work2/07939/tg872382/stampede2/connectome/stampede2/cognitive_GPS/Experiment_Bpath.RData')

CP_Ab_cryst <- CP_Moderated_Mediation("nihtbx_cryst_uncorrected","Ab",1000)
print("CP_Ab_cryst done")
CP_Ab_total <- CP_Moderated_Mediation("nihtbx_totalcomp_uncorrected","Ab",1000)
print("CP_Ab_total done")
CP_Ab_fluid <- CP_Moderated_Mediation("nihtbx_fluidcomp_uncorrected","Ab",1000)
print("CP_Ab_fluid done")


CP_Ne_cryst <- CP_Moderated_Mediation("nihtbx_cryst_uncorrected","Ne",1000)
print("CP_Ne_cryst done")
CP_Ne_total <- CP_Moderated_Mediation("nihtbx_totalcomp_uncorrected","Ne",1000)
print("CP_Ne_total done")
CP_Ne_fluid <- CP_Moderated_Mediation("nihtbx_fluidcomp_uncorrected","Ne",1000)
print("CP_Ne_fluid done")

CP_HC_all_cryst <- CP_Moderated_Mediation("nihtbx_cryst_uncorrected","HC_all",1000)
print("CP_HC_all_cryst done")
CP_HC_all_total <- CP_Moderated_Mediation("nihtbx_totalcomp_uncorrected","HC_all",1000)
print("CP_HC_all_total done")
CP_HC_all_fluid <- CP_Moderated_Mediation("nihtbx_fluidcomp_uncorrected","HC_all",1000)
print("CP_HC_all_fluid done")

save.image('/work2/07939/tg872382/stampede2/connectome/stampede2/cognitive_GPS/Experiment_Bpath.RData')

print('all done')

## ============= ##
```

#running moderated mediation. sub scale and A path 
```{r}
source('/work2/07939/tg872382/stampede2/connectome/stampede2/cognitive_GPS/MM_function.R')

## === crystallized intelligence === ##
EA_Ab_SA_cryst <- EA_Moderated_Mediation("nihtbx_cryst_uncorrected","Ab_SA",1000)
EA_Ab_PA_cryst <- EA_Moderated_Mediation("nihtbx_cryst_uncorrected","Ab_PA",1000)
print("EA_Ab_cryst done")



EA_Ne_EN_cryst <- EA_Moderated_Mediation("nihtbx_cryst_uncorrected","Ne_EN",1000)
EA_Ne_PN_cryst <- EA_Moderated_Mediation("nihtbx_cryst_uncorrected","Ne_PN",1000)
print("EA_Ne_cryst done")

EA_HC_MIH_cryst <- EA_Moderated_Mediation("nihtbx_cryst_uncorrected","HC_MIH",1000)
EA_HC_MTV_cryst <- EA_Moderated_Mediation("nihtbx_cryst_uncorrected","HC_MTV",1000)
EA_HC_HSA_cryst <- EA_Moderated_Mediation("nihtbx_cryst_uncorrected","HC_HSA",1000)
EA_HC_CHM_cryst <- EA_Moderated_Mediation("nihtbx_cryst_uncorrected","HC_CHM",1000)
#EA_HC_PSD_cryst <- EA_Moderated_Mediation("nihtbx_cryst_uncorrected","HC_PSD",10)
print("EA_HC_all_cryst done")

save.image('/work2/07939/tg872382/stampede2/connectome/stampede2/cognitive_GPS/Experiment_sub_cryst.RData')



CP_Ab_SA_cryst <- CP_Moderated_Mediation("nihtbx_cryst_uncorrected","Ab_SA",1000)
CP_Ab_PA_cryst <- CP_Moderated_Mediation("nihtbx_cryst_uncorrected","Ab_PA",1000)
print("CP_Ab_cryst done")



CP_Ne_EN_cryst <- CP_Moderated_Mediation("nihtbx_cryst_uncorrected","Ne_EN",1000)
CP_Ne_PN_cryst <- CP_Moderated_Mediation("nihtbx_cryst_uncorrected","Ne_PN",1000)
print("CP_Ne_cryst done")

CP_HC_MIH_cryst <- CP_Moderated_Mediation("nihtbx_cryst_uncorrected","HC_MIH",1000)
CP_HC_MTV_cryst <- CP_Moderated_Mediation("nihtbx_cryst_uncorrected","HC_MTV",1000)
CP_HC_HSA_cryst <- CP_Moderated_Mediation("nihtbx_cryst_uncorrected","HC_HSA",1000)
CP_HC_CHM_cryst <- CP_Moderated_Mediation("nihtbx_cryst_uncorrected","HC_CHM",1000)
#CP_HC_PSD_cryst <- CP_Moderated_Mediation("nihtbx_cryst_uncorrected","HC_PSD",10)
print("CP_HC_all_cryst done")
save.image('/work2/07939/tg872382/stampede2/connectome/stampede2/cognitive_GPS/Experiment_sub_cryst.RData')

print('all done')

## ============= ##

## === fluid intelligence === ##
EA_Ab_SA_fluid <- EA_Moderated_Mediation("nihtbx_fluidcomp_uncorrected","Ab_SA",1000)
EA_Ab_PA_fluid <- EA_Moderated_Mediation("nihtbx_fluidcomp_uncorrected","Ab_PA",1000)
print("EA_Ab_cryst done")



EA_Ne_EN_fluid <- EA_Moderated_Mediation("nihtbx_fluidcomp_uncorrected","Ne_EN",1000)
EA_Ne_PN_fluid <- EA_Moderated_Mediation("nihtbx_fluidcomp_uncorrected","Ne_PN",1000)
print("EA_Ne_cryst done")

EA_HC_MIH_fluid <- EA_Moderated_Mediation("nihtbx_fluidcomp_uncorrected","HC_MIH",1000)
EA_HC_MTV_fluid <- EA_Moderated_Mediation("nihtbx_fluidcomp_uncorrected","HC_MTV",1000)
EA_HC_HSA_fluid <- EA_Moderated_Mediation("nihtbx_fluidcomp_uncorrected","HC_HSA",1000)
EA_HC_CHM_fluid <- EA_Moderated_Mediation("nihtbx_fluidcomp_uncorrected","HC_CHM",1000)
#EA_HC_PSD_fluid <- EA_Moderated_Mediation("nihtbx_fluidcomp_uncorrected","HC_PSD",10)
print("EA_HC_all_cryst done")

save.image('/work2/07939/tg872382/stampede2/connectome/stampede2/cognitive_GPS/Experiment_sub_fluid.RData')



CP_Ab_SA_fluid <- CP_Moderated_Mediation("nihtbx_fluidcomp_uncorrected","Ab_SA",1000)
CP_Ab_PA_fluid <- CP_Moderated_Mediation("nihtbx_fluidcomp_uncorrected","Ab_PA",1000)
print("CP_Ab_cryst done")



CP_Ne_EN_fluid <- CP_Moderated_Mediation("nihtbx_fluidcomp_uncorrected","Ne_EN",1000)
CP_Ne_PN_fluid <- CP_Moderated_Mediation("nihtbx_fluidcomp_uncorrected","Ne_PN",1000)
print("CP_Ne_cryst done")

CP_HC_MIH_fluid <- CP_Moderated_Mediation("nihtbx_fluidcomp_uncorrected","HC_MIH",1000)
CP_HC_MTV_fluid <- CP_Moderated_Mediation("nihtbx_fluidcomp_uncorrected","HC_MTV",1000)
CP_HC_HSA_fluid <- CP_Moderated_Mediation("nihtbx_fluidcomp_uncorrected","HC_HSA",1000)
CP_HC_CHM_fluid <- CP_Moderated_Mediation("nihtbx_fluidcomp_uncorrected","HC_CHM",1000)
#CP_HC_PSD_fluid <- CP_Moderated_Mediation("nihtbx_fluidcomp_uncorrected","HC_PSD",10)
print("CP_HC_all_cryst done")
save.image('/work2/07939/tg872382/stampede2/connectome/stampede2/cognitive_GPS/Experiment_sub_fluid.RData')

print('all done')
## ============= ##

## === total intelligence === ##
EA_Ab_SA_total <- EA_Moderated_Mediation("nihtbx_totalcomp_uncorrected","Ab_SA",1000)
EA_Ab_PA_total <- EA_Moderated_Mediation("nihtbx_totalcomp_uncorrected","Ab_PA",1000)
print("EA_Ab_cryst done")



EA_Ne_EN_total <- EA_Moderated_Mediation("nihtbx_totalcomp_uncorrected","Ne_EN",1000)
EA_Ne_PN_total <- EA_Moderated_Mediation("nihtbx_totalcomp_uncorrected","Ne_PN",1000)
print("EA_Ne_cryst done")

EA_HC_MIH_total <- EA_Moderated_Mediation("nihtbx_totalcomp_uncorrected","HC_MIH",1000)
EA_HC_MTV_total <- EA_Moderated_Mediation("nihtbx_totalcomp_uncorrected","HC_MTV",1000)
EA_HC_HSA_total <- EA_Moderated_Mediation("nihtbx_totalcomp_uncorrected","HC_HSA",1000)
EA_HC_CHM_total <- EA_Moderated_Mediation("nihtbx_totalcomp_uncorrected","HC_CHM",1000)
#EA_HC_PSD_total <- EA_Moderated_Mediation("nihtbx_totalcomp_uncorrected","HC_PSD",10)
print("EA_HC_all_cryst done")

save.image('/work2/07939/tg872382/stampede2/connectome/stampede2/cognitive_GPS/Experiment_sub_total.RData')



CP_Ab_SA_total <- CP_Moderated_Mediation("nihtbx_totalcomp_uncorrected","Ab_SA",1000)
CP_Ab_PA_total <- CP_Moderated_Mediation("nihtbx_totalcomp_uncorrected","Ab_PA",1000)
print("CP_Ab_cryst done")



CP_Ne_EN_total <- CP_Moderated_Mediation("nihtbx_totalcomp_uncorrected","Ne_EN",1000)
CP_Ne_PN_total <- CP_Moderated_Mediation("nihtbx_totalcomp_uncorrected","Ne_PN",1000)
print("CP_Ne_cryst done")

CP_HC_MIH_total <- CP_Moderated_Mediation("nihtbx_totalcomp_uncorrected","HC_MIH",1000)
CP_HC_MTV_total <- CP_Moderated_Mediation("nihtbx_totalcomp_uncorrected","HC_MTV",1000)
CP_HC_HSA_total <- CP_Moderated_Mediation("nihtbx_totalcomp_uncorrected","HC_HSA",1000)
CP_HC_CHM_total <- CP_Moderated_Mediation("nihtbx_totalcomp_uncorrected","HC_CHM",1000)
#CP_HC_PSD_total <- CP_Moderated_Mediation("nihtbx_totalcomp_uncorrected","HC_PSD",10)
print("CP_HC_all_cryst done")
save.image('/work2/07939/tg872382/stampede2/connectome/stampede2/cognitive_GPS/Experiment_sub_total.RData')

print('all done')
## ============= ##

```


#running moderated mediation. sub scale and B path 
```{r}
source('/work2/07939/tg872382/stampede2/connectome/stampede2/cognitive_GPS/MM_function_Bpath.R')

## === crystallized intelligence === ##
EA_Ab_PA_cryst <- EA_Moderated_Mediation("nihtbx_cryst_uncorrected","Ab_PA",1000)
EA_Ab_SA_cryst <- EA_Moderated_Mediation("nihtbx_cryst_uncorrected","Ab_SA",1000)
print("EA_Ab_cryst done")



EA_Ne_PN_cryst <- EA_Moderated_Mediation("nihtbx_cryst_uncorrected","Ne_PN",1000)
EA_Ne_EN_cryst <- EA_Moderated_Mediation("nihtbx_cryst_uncorrected","Ne_EN",1000)
print("EA_Ne_cryst done")


EA_HC_MTV_cryst <- EA_Moderated_Mediation("nihtbx_cryst_uncorrected","HC_MTV",1000)
EA_HC_MIH_cryst <- EA_Moderated_Mediation("nihtbx_cryst_uncorrected","HC_MIH",1000)
#EA_HC_PSD_cryst <- EA_Moderated_Mediation("nihtbx_cryst_uncorrected","HC_PSD",10)
EA_HC_CHM_cryst <- EA_Moderated_Mediation("nihtbx_cryst_uncorrected","HC_CHM",1000)
EA_HC_HSA_cryst <- EA_Moderated_Mediation("nihtbx_cryst_uncorrected","HC_HSA",1000)
print("EA_HC_all_cryst done")

save.image('/work2/07939/tg872382/stampede2/connectome/stampede2/cognitive_GPS/Experiment_Bpath_sub_cryst.RData')

CP_Ab_PA_cryst <- CP_Moderated_Mediation("nihtbx_cryst_uncorrected","Ab_PA",1000)
CP_Ab_SA_cryst <- CP_Moderated_Mediation("nihtbx_cryst_uncorrected","Ab_SA",1000)
print("EA_Ab_cryst done")



CP_Ne_PN_cryst <- CP_Moderated_Mediation("nihtbx_cryst_uncorrected","Ne_PN",1000)
CP_Ne_EN_cryst <- CP_Moderated_Mediation("nihtbx_cryst_uncorrected","Ne_EN",1000)
print("EA_Ne_cryst done")


CP_HC_MTV_cryst <- CP_Moderated_Mediation("nihtbx_cryst_uncorrected","HC_MTV",1000)
CP_HC_MIH_cryst <- CP_Moderated_Mediation("nihtbx_cryst_uncorrected","HC_MIH",1000)
#CP_HC_PSD_cryst <- CP_Moderated_Mediation("nihtbx_cryst_uncorrected","HC_PSD",10)
CP_HC_CHM_cryst <- CP_Moderated_Mediation("nihtbx_cryst_uncorrected","HC_CHM",1000)
CP_HC_HSA_cryst <- CP_Moderated_Mediation("nihtbx_cryst_uncorrected","HC_HSA",1000)
print("EA_HC_all_cryst done")
save.image('/work2/07939/tg872382/stampede2/connectome/stampede2/cognitive_GPS/Experiment_Bpath_sub_cryst.RData')

print('all done')
## ============= ##


## === fluid intelligence === ##
EA_Ab_PA_fluid <- EA_Moderated_Mediation("nihtbx_fluidcomp_uncorrected","Ab_PA",1000)
EA_Ab_SA_fluid <- EA_Moderated_Mediation("nihtbx_fluidcomp_uncorrected","Ab_SA",1000)
print("EA_Ab_cryst done")



EA_Ne_PN_fluid <- EA_Moderated_Mediation("nihtbx_fluidcomp_uncorrected","Ne_PN",1000)
EA_Ne_EN_fluid <- EA_Moderated_Mediation("nihtbx_fluidcomp_uncorrected","Ne_EN",1000)
print("EA_Ne_cryst done")


EA_HC_MTV_fluid <- EA_Moderated_Mediation("nihtbx_fluidcomp_uncorrected","HC_MTV",1000)
EA_HC_MIH_fluid <- EA_Moderated_Mediation("nihtbx_fluidcomp_uncorrected","HC_MIH",1000)
#EA_HC_PSD_fluid <- EA_Moderated_Mediation("nihtbx_fluidcomp_uncorrected","HC_PSD",10)
EA_HC_CHM_fluid <- EA_Moderated_Mediation("nihtbx_fluidcomp_uncorrected","HC_CHM",1000)
EA_HC_HSA_fluid <- EA_Moderated_Mediation("nihtbx_fluidcomp_uncorrected","HC_HSA",1000)
print("EA_HC_all_cryst done")

save.image('/work2/07939/tg872382/stampede2/connectome/stampede2/cognitive_GPS/Experiment_Bpath_sub_fluid.RData')

CP_Ab_PA_fluid <- CP_Moderated_Mediation("nihtbx_fluidcomp_uncorrected","Ab_PA",1000)
CP_Ab_SA_fluid <- CP_Moderated_Mediation("nihtbx_fluidcomp_uncorrected","Ab_SA",1000)
print("EA_Ab_cryst done")



CP_Ne_PN_fluid <- CP_Moderated_Mediation("nihtbx_fluidcomp_uncorrected","Ne_PN",1000)
CP_Ne_EN_fluid <- CP_Moderated_Mediation("nihtbx_fluidcomp_uncorrected","Ne_EN",1000)
print("EA_Ne_cryst done")


CP_HC_MTV_fluid <- CP_Moderated_Mediation("nihtbx_fluidcomp_uncorrected","HC_MTV",1000)
CP_HC_MIH_fluid <- CP_Moderated_Mediation("nihtbx_fluidcomp_uncorrected","HC_MIH",1000)
#CP_HC_PSD_fluid <- CP_Moderated_Mediation("nihtbx_fluidcomp_uncorrected","HC_PSD",10)
CP_HC_CHM_fluid <- CP_Moderated_Mediation("nihtbx_fluidcomp_uncorrected","HC_CHM",1000)
CP_HC_HSA_fluid <- CP_Moderated_Mediation("nihtbx_fluidcomp_uncorrected","HC_HSA",1000)
print("EA_HC_all_cryst done")
save.image('/work2/07939/tg872382/stampede2/connectome/stampede2/cognitive_GPS/Experiment_Bpath_sub_fluid.RData')

print('all done')

## ============= ##


## === total intelligence === ##
EA_Ab_PA_total <- EA_Moderated_Mediation("nihtbx_totalcomp_uncorrected","Ab_PA",1000)
EA_Ab_SA_total <- EA_Moderated_Mediation("nihtbx_totalcomp_uncorrected","Ab_SA",1000)
print("EA_Ab_cryst done")



EA_Ne_PN_total <- EA_Moderated_Mediation("nihtbx_totalcomp_uncorrected","Ne_PN",1000)
EA_Ne_EN_total <- EA_Moderated_Mediation("nihtbx_totalcomp_uncorrected","Ne_EN",1000)
print("EA_Ne_cryst done")


EA_HC_MTV_total <- EA_Moderated_Mediation("nihtbx_totalcomp_uncorrected","HC_MTV",1000)
EA_HC_MIH_total <- EA_Moderated_Mediation("nihtbx_totalcomp_uncorrected","HC_MIH",1000)
#EA_HC_PSD_total <- EA_Moderated_Mediation("nihtbx_totalcomp_uncorrected","HC_PSD",10)
EA_HC_CHM_total <- EA_Moderated_Mediation("nihtbx_totalcomp_uncorrected","HC_CHM",1000)
EA_HC_HSA_total <- EA_Moderated_Mediation("nihtbx_totalcomp_uncorrected","HC_HSA",1000)
print("EA_HC_all_cryst done")

save.image('/work2/07939/tg872382/stampede2/connectome/stampede2/cognitive_GPS/Experiment_Bpath_sub_total.RData')

CP_Ab_PA_total <- CP_Moderated_Mediation("nihtbx_totalcomp_uncorrected","Ab_PA",1000)
CP_Ab_SA_total <- CP_Moderated_Mediation("nihtbx_totalcomp_uncorrected","Ab_SA",1000)
print("EA_Ab_cryst done")



CP_Ne_PN_total <- CP_Moderated_Mediation("nihtbx_totalcomp_uncorrected","Ne_PN",1000)
CP_Ne_EN_total <- CP_Moderated_Mediation("nihtbx_totalcomp_uncorrected","Ne_EN",1000)
print("EA_Ne_cryst done")


CP_HC_MTV_total <- CP_Moderated_Mediation("nihtbx_totalcomp_uncorrected","HC_MTV",1000)
CP_HC_MIH_total <- CP_Moderated_Mediation("nihtbx_totalcomp_uncorrected","HC_MIH",1000)
#CP_HC_PSD_total <- CP_Moderated_Mediation("nihtbx_totalcomp_uncorrected","HC_PSD",10)
CP_HC_CHM_total <- CP_Moderated_Mediation("nihtbx_totalcomp_uncorrected","HC_CHM",1000)
CP_HC_HSA_total <- CP_Moderated_Mediation("nihtbx_totalcomp_uncorrected","HC_HSA",1000)
print("EA_HC_all_cryst done")
save.image('/work2/07939/tg872382/stampede2/connectome/stampede2/cognitive_GPS/Experiment_Bpath_sub_total.RData')

print('all done')
## ============= ##

```

